A summary on Delta Debugging and its uses

### 2019-01-02 Paper/article.tex
Minor fixes in the algorithms chapter.

\definition \defsub{Complement of configuration} Let $c \subseteq \C$ be a configuration. The configuration $\bar{c} = \C \setminus c$ is called the \textbf{complement} of $c$.\\

@@

\begin{algorithmic}[1]
	\Function{$dd_3$}{$c,r:2^\C, n: \nN$} $: 2^{\C}$
	\State let $c_1,\dots,c_n \subseteq c \text{ with } \bigcup c_i = c, c_i \text{ pairwise disjoint}, \forall i: |c_i| \approx |c|/n$
	\State let $\bar{c_i} = c \setminus (c_i \cup r), t_i = test(c_i \cup r), \bar{t_i} = test(\bar{c_i} \cup r)$
	\State let $c' = c \cap \bigcap \set{\bar{c_i} \mid \bar{t_i} = \xmark}, r' = r \cup \bigcup \set{c_i \mid t_i = \cmark}, n' = min (\mid c' \mid, 2n)$
	\State let $d_i = dd_3(c_i, \bar{c_i} \cup r, 2), \bar{d_i} = dd_3(\bar{c_i},c_i \cup r, 2)$ 
	\State \Return $ \begin{cases}
			c & \text{if } |c|=1, \text{\Comment("Found")}\\
			dd_3(c_i, r, 2) & \text{if } t_i = \xmark \text{ for some i \Comment("Found in $c_i$")}\\
			d_i \cup \bar{d_i} & \text{if } t_i = \cmark \wedge \bar{t_i} = \cmark \text{ for some i \Comment("Interference")}\\
			d_i & \text{if } t_i = \qmark \wedge \bar{t_i} = \cmark \text{ for some i \Comment("Preference")}\\
			dd_3(c',r',n') & \text{if } n < \mid c \mid \text{\Comment("Try Again")}\\
			c' & \text{otherwise \Comment("nothing left")}
		\end{cases}$
	\EndFunction
\end{algorithmic}
\end{minipage}}
\caption{The \ddp\ algorithm capable of dealing with unresolved test cases.}
\end{figure}

>>>>

\definition \defsub{Complement of configuration} Let $c \subseteq \C$ be a configuration. The configuration $\bar{c}$ is called the \textbf{complement} of $c$. It contains all changes that are contained in the current search but not in $c$.\\

@@

\begin{algorithmic}[1]
	\Function{$dd_3$}{$c,r:2^\C, n: \nN$} $: 2^{\C}$
	\State let $c_1,\dots,c_n \subseteq c \text{ with } \bigcup c_i = c, c_i \text{ pairwise disjoint}, \forall i: |c_i| \approx |c|/n$
	\State let $\bar{c_i} = c \setminus (c_i \cup r), t_i = test(c_i \cup r), \bar{t_i} = test(\bar{c_i} \cup r)$
	\State let $c' = c \cap \bigcap \set{\bar{c_i} \mid \bar{t_i} = \xmark}, r' = r \cup \bigcup \set{c_i \mid t_i = \cmark}, n' = min (\mid c' \mid, 2n)$
	\State let $d_i = dd_3(c_i, \bar{c_i} \cup r, 2), \bar{d_i} = dd_3(\bar{c_i},c_i \cup r, 2)$ 
	\State \Return $ \begin{cases}
			c & \text{if } |c|=1, \text{\Comment("Found")}\\
			dd_3(c_i, r, 2) & \text{if } t_i = \xmark \text{ for some i \Comment("Found in $c_i$")}\\
			d_i \cup \bar{d_i} & \text{if } t_i = \cmark \wedge \bar{t_i} = \cmark \text{ for some i \Comment("Interference")}\\
			d_i & \text{if } t_i = \qmark \wedge \bar{t_i} = \cmark \text{ for some i \Comment("Preference")}\\
			dd_3(c',r',n') & \text{if } n < \mid c \mid \text{\Comment("Try Again")}\\
			c' & \text{otherwise \Comment("Nothing Left")}
		\end{cases}$
	\EndFunction
\end{algorithmic}
\end{minipage}}
\caption{The \ddp\ algorithm capable of dealing with unresolved test cases.}
\end{figure}
